intro

### 2022-08-09 06_Paper/ER-ED/ERED_Stage2/method.Rmd
added comma

*Effects of emotion regulation on arousal, facial EMG and effort.* <br> 
To investigate the effects of the three ER strategies on subjective arousal (H2a), another rmANOVA  with the factor strategy (active viewing - negative, distraction, distancing, and suppression) for subjective arousal ratings was conducted.
To examine the effects of the three ER strategies on physiological responding (H3a and H3b), another rmANOVA with the factor strategy (active viewing - negative, distraction, distancing, and suppression) for EMG *corrugator* and *levator* activity was conducted.
To examine the effect of ER strategies on subjective effort (H4a), a rmANOVA with the factor strategy (active viewing - negative, distraction, distancing, and suppression) for subjective effort ratings was conducted.

>>>>

*Effects of emotion regulation on arousal, facial EMG, and effort.* <br> 
To investigate the effects of the three ER strategies on subjective arousal (H2a), another rmANOVA  with the factor strategy (active viewing - negative, distraction, distancing, and suppression) for subjective arousal ratings was conducted.
To examine the effects of the three ER strategies on physiological responding (H3a and H3b), another rmANOVA with the factor strategy (active viewing - negative, distraction, distancing, and suppression) for EMG *corrugator* and *levator* activity was conducted.
To examine the effect of ER strategies on subjective effort (H4a), a rmANOVA with the factor strategy (active viewing - negative, distraction, distancing, and suppression) for subjective effort ratings was conducted.
